%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associate Lead Software Engineer} % Job title
    {Cerner Healthcare Solutions Private Ltd.} % Organization
    {Bangalore, Karnataka} % Location
    {September 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and Implemented API discovery system for iPaaS using Spring Boot and Swagger-Parser.}
        \item {Responsible for creation of innovative ePrescription solution which reduces the impact of specification changes from Surescripts.}
        \item {Led an Agile team in taking ownership of product and software development process of OpenLink Integration Manager.}
        \item {Developed RESTful Open API for message archiving system using Spring EcoSystem.}
        \item {Developed React Components for message archiving system using ReactJS library.}
        \item {Created an Enterprise Java Server(EJS) for ePrescription Initiative.}
        \item {Built an automated testing framework for Integration testing which is utilized across the agile teams.}
        \item {Provides functional, resource planning guidance to programming, engineering, and management staff or groups.}
        \item {Identifies software engineering process improvements, and enforces the execution of them across the organization.}
      \end{cvitems}
    }
  
    \begin{cventries}
        \cventry
          {Senior Software Engineer}
          {}
          {}
          {September 2015 - August 2018}
          {
            \begin{cvitems}
              \item {Implemented JAX-RS based services for Child Protection Information System to enhance interoperability between UK clients.}
              \item {Excelled in performance testing of REST services using Gatling and JMeter.}
              \item {Reduced configuration time from over an hour to <5 minutes, allowing us to rapidly release new features and obligations.}
              \item {Created an Imitator services for UK NHS which allowed team to test on simulated NHS ennvironment.}
              \item {Led the team towards migration of version control system to Git.}
            \end{cvitems}
          }
    \end{cventries}

%---------------------------------------------------------
  \cventry
    {Associate Senior Software Engineer} % Job title
    {Continental Automotive Components (India) Pvt. Ltd,} % Organization
    {Bangalore, Karnataka} % Location
    {August. 2013 - September. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Study and analysis of project requirements, preparation of Functional Specifications, Data modeling, design and implementation.}
        \item {Involvement in technical design makings like database designing and framework.}
        \item {Created platform to control the execution of test procedures at the automotive test center.}
        \item {Developed new features for Rapla a Swing based scheduling application.}
        \item {Prepared and presented software development plans and test plans/reports to ensure projects are completed on time and on budget.}
      \end{cvitems}
    }

    \begin{cventries}
      \cventry
        {Software Engineer}
        {}
        {}
        {August 2010 - August 2013}
        {
          \begin{cvitems}
            \item {Built an easy-to-use CMS application for Innovation committe using Rapid application development.}
            \item {Implemented modular plugins and RCP based Infopool application for Testbench operations.}
            \item {Created complex widgets for Tools management application using SWT/JFace.}
            \item {Increased the productivity of automotive testing team by creating build scripts, command line interfaces, and other tools to support their work.}
            \item {To analyze issues, expedite innovative solutions and consensus-driven environment that contributes to on-quality, on-time project delivery.}
          \end{cvitems}
        }
    \end{cventries}

%---------------------------------------------------------
\end{cventries}
